Curve counting in genus one: elliptic singularities and relative geometry

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

For let us choose a component $C_i^\prime$ of the curve which lies on the radius. Then $\OO(\delta)$ can be expressed as a tensor product of tangent line bundles along the path connecting $C_i^\prime$ to the core. However, this lage product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally isomorphic \ref{VZ}. Thus the product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side. Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ has degenerated). Thus we obtain the universal tangent line bundle $\TT_{C_0}$ as the contribution to the right-hand side.

>>>>

For let us choose a component $C_i^\prime$ of the curve which lies on the radius. Then $\OO(\delta)$ can be expressed as a tensor product of tangent line bundles along the path connecting $C_i^\prime$ to the core. However, this lage product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other \cite{VZ}. Thus these terms cancel, and product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side. Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ has degenerated). Thus we obtain the universal tangent line bundle $\TT_{C_0}$ as the contribution to the right-hand side.
